A Physically Motivated Framework to Compare Merger Timescales\\ of Isolated Low- and High-Mass Galaxy Pairs Across Cosmic Time

### 2024-03-22 paper/main.tex
Updates from Overleaf

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{plots/bet-on-it/3_time_til_merger_full_fit.png}
    \caption{\kc{TODO: add LookbackTime vs. Z line, add Hubble time line} The median time until merger as a function of redshift for low-mass (green) and high-mass (pink) pairs. Shaded regions represent the 1st and 3rd quartile spread on the median. Pairs at each redshift are selected if they have experienced first infall. 
    % 
    The black dashed line shows the Hubble time, which bounds the median time until merger from $z=6$ to $z\sim0.5-0.75$.
    The dotted grey line shows the time to $z=0$ (the Lookback Time) as a function of redshift, which sets the upper bound for the time until merger that a merging pair can have. 
    The median time until merger is similar for low-mass and high-mass pairs, and rises from $z=6$ to a peak at $z\sim0.75$, then decreases to $z=0$.}
    \label{fig:timescales}
\end{figure*}

@@

@@

% set of conclusions for discussion
- We find that the merger timescale of low-mass or high-mass merging pairs is sensitive to the selection criteria that are used to define the pair sample.
- We recommend that future studies that seek to compare or compute pair fractions, merger fractions, merger timescales, or merger rates, define selected pair samples using separation criteria that evolve with redshift and mass.

>>>>

\begin{figure*}[htb]
    \centering
    \includegraphics[width=0.9\textwidth]{plots/bet-on-it/3_time_til_merger_full_fit.png}
    \caption{\kc{TODO: add LookbackTime vs. Z line, add Hubble time line} The median time until merger as a function of redshift for low-mass (green) and high-mass (pink) pairs. Shaded regions represent the 1st and 3rd quartile spread on the median. Pairs at each redshift are selected if they have experienced first infall. 
    % 
    The black dashed line shows the Hubble time, which bounds the median time until merger from $z=6$ to $z\sim0.5-0.75$.
    The dotted grey line shows the time to $z=0$ (the Lookback Time) as a function of redshift, which sets the upper bound for the time until merger that a merging pair can have. 
    The median time until merger is similar for low-mass and high-mass pairs, and rises from $z=6$ to a peak at $z\sim0.75$, then decreases to $z=0$.}
    \label{fig:timescales}
\end{figure*}

@@

maybe a point: 
For things that don't merge, what's... going on?

@@

% set of conclusions for discussion
- We find that the merger timescale of low-mass or high-mass merging pairs is sensitive to the selection criteria that are used to define the pair sample.\\

- We recommend that future studies that seek to compare or compute pair fractions, merger fractions, merger timescales, or merger rates, define selected pair samples using separation criteria that evolve with redshift and mass.
